\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{casual}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\firstname{Corentin}
\familyname{Dupont}
\title{Senior Researcher}
\address{via Villa Belfonte, 7}{38123 Trento}
\mobile{+39 380 6312093}
\email{corentin.dupont@gmail.com}
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{On-Going (3rd year)}{PhD}{University of Trento}{Trento}{}{Thesis on energy management in data centres}
\cventry{2003}{MsD}{Institut Supérieur de l'Electronique et du Numérique}{Toulon}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

\section{Experience}
\cventry{2010--present}{Work Package manager}{Create-Net}{Trento}{}{Leader of Work Package 4 (FIT4Green) and 5 (DC4Cities). Research and design the algorithms and policies for energy-aware optimization of data centre operations.
\begin{itemize}
  \item	WP management,
  \item Algorithmic research, specification and design,
  \item Implementation of FIT4Green prototype using Constraint Programming,
  \item Paper writing and project proposal writing.
\end{itemize}
}
\cventry{2011--2012}{Researcher}{Create-Net}{Trento}{}{Research in the area of Internet of Things. Leader of the iCore platform.
\begin{itemize}
  \item Research on DSLs to address the diversity of real-world objects,
  \item Implementation of the iCore platform prototype,
  \item Coordination of the implementation of the platform.
\end{itemize}
}
\cventry{2003--2008}{Project Leader}{DCNS/EADS}{Aix en Provence, France}{}{Projects for the Norway frigates SKJOLD and the Franco-Italian frigates HORIZON
\begin{itemize}
  \item Technical leader and project leader (CMMi 3), with a team of 4 persons for the realization of the Real Time Simulator (DCNS)
  \item Specification, Conception and development of 5 simulators (calculator in Ada and GUI in C++/Qt) : Fire Control Tracker, Decoy Launcher System, Torpedo Launch System, Air Transceiver, Principal Anti-Air Missile System.
  \item Evolution of NeVis, a 3D demonstrator for urban warfare (EADS).
\end{itemize}
C++, Ada, Qt, Linux, CMMi tools, OWB, Doors, Vega Prime, Delta 3D
}

\cventry{2009--2010}{Sofware Leader}{PSA Peugeot-Citroën}{Paris, France}{}{Supplier’s management for the automatic gearbox AL4/AT8 for PSA Peugeot Citroën
\begin{itemize}
  \item Specification writing
  \item Management of the supplier (evolutions, technical issues, project management).
\end{itemize}
MS-Project, project management tools, SQL.
}


\section{Languages}
\cvlanguage{English}{Fluent}{647/700 TOEFL, 980/990 TOEIC, work \& everyday language}
\cvlanguage{Italian}{Fluent}{living in Italy since 2010}
\cvlanguage{French}{Native}{}

\section{Computer skills}
\cvcomputer{Operating Systems}{Linux, Windows, Solaris, HP-UX}{Languages}{Haskell, Java, C++, Ada}
\cvcomputer{Programming techniques}{Constraint Programming, Big Data: Hadoop}{Development and Specification}{Eclipse, Linux tools, Qt, Doors}
\cvcomputer{Project Management}{CMMi 3 level, MS Project, OWB}{category 6}{XXX, YYY, ZZZ}

\section{Interests}
\cvline{Paragliding}{\small Flying since 20 years, licenced for taking passengers}
\cvline{Hacking}{\small Author of a unique game called Nomyx: www.nomyx.net}
\cvline{Language learning}{\small Spanish, Czech}

\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.
